Minicaml, a purely functional, didactical programming language with an interactive REPL.

### 2019-12-23 paper/paper.tex
paper

\section{AST Optimization}
Before being evaluated, AST expressions are analyzed and optimized by an
optimizer function that is recursively called over the tree that is representing
the expression. To achieve minimization to an unreducible (not optimizable)
form, optimizer calls are iterated on each previous call's result; this way,
when a tree representing an expression cannot be optimized again.
This is the process represented in pseudo-code:

@@

\section{Thanks}
Thanks to Antonio DeLucreziis for helping me introduce lazy evaluation.

>>>>

\section{AST Optimization}
Before being evaluated, AST expressions are analyzed and optimized by an
optimizer function that is recursively called over the tree that is representing
the expression. The optimizer simplifies expressions which result is known and
therefore does not need to be evaluated. For example, it is known that \texttt{5
+ 3 $\equiv$ 8} and \texttt{true \&\& (true || (false \&\& false)) $\equiv$
true}. When a programmer writes a program, she or he may not want to do all the
simple calculations before writing the program in which they appear in, we rely
on machines to simplify those processes. Reducing constants before evalaution
may seem unnecessary when writing a small program, but they do take away
computation time, and if they appear inside of loops, it is a wise choice to
simplify those constant expressions whose result is already known before it is
calculated in all the loop iterations. To achieve minimization to an unreducible form, optimizer calls are iterated on
each previous call's result; this way, we get a tree representing an expression
that cannot be optimized again. This process is fairly easy:

\begin{lstlisting}[style=caml]
let rec iterate_optimizer e =
	let oe = optimize e in
	if oe = e then e (* Bottoms out *)
	else iterate_optimizer oe
\end{lstlisting}

@@

\section{Thanks}
Thanks to Antonio DeLucreziis for helping me implement lazy evaluation.
